---
title: "Using texPreview with tikz"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using texPreview with tikz}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = !nzchar(Sys.getenv("NOT_CRAN"))
)
```

texPreview can be used for any TeX input beyond tabular environments, such as `tikz`. In the following examples we input a `tikzpicture` and an entire TeX file that contains a `tikz` environment.

```{r setup}
library(texPreview)

```
 
```{r}
# add tikz support to tex_opts

use_lib <- "\\usetikzlibrary{arrows,shapes,snakes,automata,backgrounds,arrows.meta,positioning}"

tex_opts$set(
  returnType  = 'html',
  usrPackages = build_usepackage(pkg = 'tikz',uselibrary = use_lib)
)

```
 
```{r}
tikz_examples <- list.files(system.file('examples/tikz',package = 'texPreview'),
                          pattern = 'tex$',full.names = TRUE)

tikz_code <- lapply(tikz_examples,
                    function(x) paste0(readLines(x),collapse = '\n'))

names(tikz_code) <- basename(tikz_examples)

```

## tikzpicture

```{r}
tex_preview(obj = tikz_code$pk_model.tex)
```
 
```{r,echo=FALSE}
details::details(tikz_code$pd_model.tex,summary = 'Click to view TeX',lang = 'tex')
```

## File

For a full TeX document use the `tex_lines` argument instead of the `obj`. This input bypasses the internal document template that is used for texPreview and renders the contents of the file directly. 

```{r}
tex_preview(tex_lines = tikz_code$credit_rationing.tex)
```

```{r,echo=FALSE}
details::details(tikz_code$credit_rationing.tex,summary = 'Click to view TeX',lang = 'tex')
```
